|

### 2021-06-07 01-Chp-Background.Rmd
End of day: -2964

### Lipid fractions

@@

<!----------------------------------------------------------------------------->
### Triangulating across study designs

@@

@@

_**McGuinness, L. A.**, and L Schmidt. (2020) medrxivr: Accessing and searching medRxiv and bioRxiv preprint data in R." Journal of Open Source Software 5.54 2651. DOI: [10.21105/joss.02651](https://doi.org/10.21105/joss.02651)_

A paper introducing the open-source preprint search tool described in Chapter \@ref(sys-rev-tools-heading). As is common for journal articles describing software, the paper is intentionally short providing only a broad overview of the tool while extensive documentation is available from the project website (see \@ref(sys-rev-tools-intro) for more details).

@@

The experience of extracting data for the systematic review in Chapter \@ref(sys-rev-heading) inspired a practical guide for researchers. This piece was co-written with Dr. Emily Hennessy (see Author Declarations in the front materials). [Under 2nd round of review at Prevention Science]

@@

_**McGuinness, L. A.**, and Sheppard A. L. 2020. “A Descriptive Analysis of the Data Availability Statements Accompanying Medrxiv Preprints and a Comparison with Their Published Counterparts.” MetaArXiv. DOI: [10.31222/osf.io/p75xe](https://doi.org/10.31222/osf.io/p75xe)_

Using the tool described in Chapter \@ref(sys-rev-tools), I lead a "research-on-research" study to assess the concordance between the data availability statements accompanying a sample of medRxiv preprints and their published counterparts. [Accepted to PLOS One - need to update the citation]

>>>>

### Lipid fractions {#intro-lipid-fractions}

@@

<!----------------------------------------------------------------------------->
### Triangulating across study designs {#intro-triangulation}

@@

<!-- TODO Ideally the two preprints for the CPRD and systematic review papers will go here -->

@@

_**McGuinness, L. A.**, and L Schmidt. (2020) medrxivr: Accessing and searching medRxiv and bioRxiv preprint data in R. Journal of Open Source Software 5.54 2651. DOI: [10.21105/joss.02651](https://doi.org/10.21105/joss.02651)_

A paper introducing the open-source preprint search tool described in Chapter \@ref(sys-rev-tools-heading). As is common for journal articles describing software, the paper is intentionally short providing only a broad overview of the tool while extensive documentation is available from the project website (see Section \@ref(sys-rev-tools-intro) for more details).

@@

The experience of extracting data for the systematic review in Chapter \@ref(sys-rev-heading) inspired a practical guide for researchers. This piece was co-written with Dr. Emily Hennessy (see Author Declarations in the front materials). <!-- TODO Need to create author declarations section -->
 [Under 2nd round of review at Prevention Science]

@@

_**McGuinness, L. A.**, and Sheppard A. L. 2020. “A Descriptive Analysis of the Data Availability Statements Accompanying Medrxiv Preprints and a Comparison with Their Published Counterparts.”  PLOS ONE 16(5): e0250887. DOI: [10.1371/journal.pone.0250887](https://doi.org/10.1371/journal.pone.0250887)_

Using the tool described in Chapter \@ref(sys-rev-tools), I lead a "research-on-research" study to assess the concordance between the openness of data availability statements accompanying a sample of medRxiv preprints and their published counterparts.

### 2021-06-07 02-Chp-Systematic-Review-Tools.Rmd
End of day: -3464
End of day: -3311
End of day: -2964

@@

@@

>>>>

<!-- TODO I might need to make it clearer thatthe tool was always intended to search both databases, as medRxiv grew out of bioRxiv categories, and no relevant records identified by the search in medRxiv -->

@@

<!-- IDEA Could remake this using Diagrammr? -->

@@

<!-- IDEA Add timeline chart as seen here: https://bookdown.org/alecri/thesis/4-methods.html#sec:dosresmeta -->

### 2021-06-07 03-Chp-Systematic-Review.Rmd
End of day: -2964

(ref:sys-rev-quote) --- Archie Cochrane, 2000 [@cochrane20001931]

@@

@@

Given the focus on triangulating different sources of evidence at risk of a diverse range of bias, a detailed and structured risk of bias assessment formed an important part of this review.

There has been a recent moved from

Talk about move from checklist tools to more domain based methods

Many reviews use reporting guidelines instead - this is bad![@costa2011]

Described here how tools work and how you get an overall judgement -. algorithm

@@

Risk of bias assessment was performed using the domain-based risk-of-bias assessment tool appropriate to the study design. Randomized controlled trials were assessed using the RoB2 tool,[@sterne2019], 
The tool assess the risk of bias across five domains: Bias arising from the randomization process, Bias due to deviations from intended intervention, Bias due to missing outcome data, Bias in measurement of the outcome, Bias in selection of the reported result.

@@

For non-randomised studies of interventions, I used the ROBINS-I (Risk of bias in non-randomised studies - of interventions) <!-- TODO Capitalise appropriately --> tool.[@sterne2016] This tool assess the risk of bias across seven domains: Bias due to confounding, Bias due to selection of participants, Bias in classification of interventions, Bias due to deviations from intended interventions, Bias due to missing data, Bias in measurement of outcomes, and Bias in selection of the reported result. Similar to the RoB 2, it has a number of prompting questions per domain, with judgements includeing. Ideally, obs studies assesed in reference to an idealised randomised controlled trial. Futher, the rare overall judgement of Low should be considered equivalent to a randomised controlled trial.

For non-randomised studies o
I opted to use the ROBINS-E tool, despite it still being in development,[@morganr2020] in place of other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000newcastle] There are two primary reasons for this: firstly, current thinking in assessing internal validity has moved away from scales.

non-randomized studies of interventions were assessed using the ROBINS-I tool, and non-randomized studies of exposures were assessed using the ROBINS-E tool.[CITE]

<!-- TODO Cite release version of this tool, and just use domain based approach -->

Secondly, as mentioned in the introduction to this section, using a domain based to assess the risk of bias in studies of exposure allowed for better comparison and consistency across the tool used for different study designs, as they are all domain based.

@@

At present, no risk of bias assessment tool for Mendelian randomization studies is available. Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk of bias assessments in systematic reviews of MR studies. A copy of this tool is available in Appendix \@ref(appendix-mr-rob). Advance results from this review of bias assessment in MR studies were obtained from contact with the authors.

@@

@@

### Statistical analysis methods

@@

@@

@@

.

@@

@@

@@

<!-- TODO Have a look at this -->

>>>>

(ref:sys-rev-quote) --- Archibald Cochrane, 2000 [@cochrane20001931]

@@

Where necessary, lipid levels reported in _mmol/L_ were converted in _mg/dL_ using the following formula:

$$
mg/dL = mmol/L \times{} Z
$$
where $Z = 38.67$ for total cholesterol, LDL-c and HDL-c, and $Z = 88.57$ for triglycerides. For widely-used categorises of lipids levels on the _mg/dL_ scale, see Table \@ref(tab:lipidLevels-table) in Section \@ref(intro-lipid-fractions).

@@

A key use of the review presented in this chapter is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(intro-triangulation) and Section \@ref(triangulation-overview) for an overview of triangulation). To enable this triangulation exercise, a detailed and structured risk of bias assessment formed an important part of this review.

There has been a recent movement within the evidence synthesis community from examining _methodological quality_ to assessing _risk of bias_,[@mcguinness2018a; @sterne2016] and thus directly evaluating the internal validity of a study. Internal validity is defined here as the absence of systematic error (or bias) in a study, which may influence its results.[@campbell1957; @juni2001]

This move was prompted by a unclear definition of "methodological quality" which could include facets such as, and challenges in the comparison of results from different tools.

As part of this, the community also moved from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order.

Additionally, results should be assessed at the result (defined as a a specific outcome at a specific timepoint) rather than the study level. For example, a study may report on the efficacy of an intervention at 6 months and two years follow-up. missing outcome data that is not an issues at 6 months may introduce bias at 2 year follow-up. In this case, assigning a bias judgement to the study as a whole hides this differential biases for each result.

In this review, domain-based tools were used to assess the risk of bias for each result in each included study. The study design-specific tools are introduced and discussed in more detail in the following sections.

@@

Risk of bias assessment in randomised controlled trials was performed using the domain-based risk-of-bias assessment tool appropriate to the study design. Randomized controlled trials were assessed using the RoB2 tool,[@sterne2019], 
The tool assess the risk of bias across five domains: Bias arising from the randomization process, Bias due to deviations from intended intervention, Bias due to missing outcome data, Bias in measurement of the outcome, Bias in selection of the reported result. Acceptable judgements include: low risk of bias, some concerns, high risk of bias. Each of the 5 domains contains a series of signalling questions or prompts, which guide the user through the tool.

One a domain-level judgement for each domain has been assigned, an overall judgement, using the same three levels of risk of bias, is assigned to

@@

For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk of bias in non-randomised studies - of interventions) <!-- TODO Capitalise appropriately --> tool.[@sterne2016] This tool assess the risk of bias across seven domains: Bias due to confounding, Bias due to selection of participants, Bias in classification of interventions, Bias due to deviations from intended interventions, Bias due to missing data, Bias in measurement of outcomes, and Bias in selection of the reported result. Similar to the RoB 2, it has a number of prompting questions per domain, with judgements including. Ideally, obs studies assessed in reference to an idealised randomised controlled trial. Further, the rare overall judgement of Low should be considered equivalent to a randomised controlled trial.

For non-randomised studies of exposures (NRSE), I opted to use a preliminary version of the ROBINS-E tool, despite it still being in development.[@morganr2020] While the signalling questions for each domain are yet to be confirmed, the overarching domains have been finalised.

Despite these limitations, I chose this approach in place of other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000newcastle] The motivation for this decision was two-fold. In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools such as the NOS. In addition, using a domain-based tool enabled better comparison with risk-of-bias assessments performed for the other study designs.

@@

At present, no risk-of-bias assessment tool for Mendelian randomization studies is available. Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk of bias assessments in systematic reviews of MR studies. A copy of this tool is available in Appendix \@ref(appendix-mr-rob). Advance results from this review of bias assessment in MR studies were obtained from contact with the authors.

@@

Use the example of getting the cut-off points from the

@@

### Analysis methods

#### Simple meta-analysis

@@

Both a fixed-effect and random-effects meta-analysis model was.

For

@@

#### Dose-response analyses

<!-- TODO Explore how to map from simple diagnosis of hyperchol to dose response. Seems that does response needs > 3 categories -->

Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g. for example, highest vs lowest quartile). while this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contain in the interim groups.

Where possible, data for all exposure groups was extracted, and this. Studies were excluded from this analysis if the number of categories was less than three, if the exposure cut-off points for for each category were not presented (e.g. if the study reports splitting participants into quartiles and comparing the highest vs lowest without giving the quartile bands in mmol/L)

Note that

#### Sensitivity analyses

&nbsp;
<!----------------------------------------------------------------------------->

@@

&nbsp;
<!----------------------------------------------------------------------------->

@@

### Dose response meta-analysis

<!-- TODO Cite excluded studies and  -->

Several studies were excluded from the dose-response meta-analysis, as the number of cases/controls be

<!-- TODO Include image -->

@@

<!-- TODO Have a look at this - potentially move to triangulation chapter -->

@@

### 2021-06-07 front-and-back-matter/99-appendices.Rmd
End of day: -2964

<!----------------------------------------------------------------------------->
## Chapter \@ref(intro-heading) {#appendix-into}

@@

  * McGuinness & Sheppard. Comparison of pairwise

@@

<!-- Essentially, look at the Trello -->
__Under review/Preprints__

@@

## Chapter \@ref(sys-rev-tools-heading) {#appendix-sys-tools}
<!----------------------------------------------------------------------------->

@@

@@

<!-- Double check this is the final code used -->

>>>>

<!----------------------------------------------------------------------------->
## Chapter \@ref(background-heading) {#appendix-into}

@@

@@

<!-- TODO update list with proper references and a description of each. Essentially, look at the Trello -->

__Under review/Preprints__

@@

## Chapter \@ref(sys-rev-heading) {#appendix-sys-rev}
<!----------------------------------------------------------------------------->

@@

Impor

@@

<!-- TODO Double check this is the final code used -->
